---
title: "Content Validity Report"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
params:
  console_out: NA
  aiken_res: NA
  cvr_res: NA
  icvi_res: NA
  scvi_res: NA
  ai_summary: ""
---

<style>
  @import url('https://fonts.googleapis.com/css2?family=Inter:wght@400;500;600;700&display=swap');
  
  body, p, table, td, th {
    font-family: 'Inter', 'Segoe UI', Roboto, Helvetica, Arial, sans-serif;
    line-height: 1.6 !important;
    font-size: 14px;
    color: #333333;
  }
  h1, h2, h3, h4, h5, h6 {
    font-family: 'Inter', 'Segoe UI', Roboto, Helvetica, Arial, sans-serif;
    line-height: 1.2;
    font-weight: 600;
    color: #2c3e50;
    margin-top: 1.5em;
    margin-bottom: 0.5em;
  }
  h1 { font-size: 28px; border-bottom: 2px solid #ecf0f1; padding-bottom: 10px; }
  h2 { font-size: 22px; color: #2980b9; }
  h3 { font-size: 18px; color: #34495e; }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
library(kableExtra)
```

## Aiken's V

```{r}
res_a <- params$aiken_res
if(!is.null(res_a)){
  df_a <- as.data.frame(res_a$df)
  df_a$Item <- rownames(res_a$df)
  df_a <- df_a[, c(ncol(df_a), 1:(ncol(df_a)-1))]
  kable(df_a, format = "html", row.names = FALSE, digits = 3) %>% 
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
}
```

## Content Validity Ratio (CVR) - Lawshe

```{r}
res_cvr <- params$cvr_res
if(!is.null(res_cvr)){
  df_cvr <- as.data.frame(res_cvr)
  df_cvr$Item <- rownames(res_cvr)
  df_cvr <- df_cvr[, c(ncol(df_cvr), 1:(ncol(df_cvr)-1))]
  kable(df_cvr, format = "html", row.names = FALSE, digits = 3) %>% 
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
}
```

## Content Validity Index (I-CVI & S-CVI)

### Item-Level CVI (I-CVI)

```{r}
res_icvi <- params$icvi_res
if(!is.null(res_icvi)){
  df_icvi <- as.data.frame(res_icvi)
  df_icvi$Item <- rownames(res_icvi)
  df_icvi <- df_icvi[, c(ncol(df_icvi), 1:(ncol(df_icvi)-1))]
  kable(df_icvi, format = "html", row.names = FALSE, digits = 3) %>% 
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
}
```

### Scale-Level CVI (S-CVI)

```{r}
res_scvi <- params$scvi_res
if(!is.null(res_scvi)){
  df_scvi <- as.data.frame(res_scvi)
  kable(df_scvi, format = "html", row.names = FALSE, digits = 3) %>% 
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
}
```

```{r ai-summary, results='asis'}
if (!is.null(params$ai_summary) && params$ai_summary != "") {
  cat("## AI Interpretive Summary\n\n")
  cat("<div style='background-color: #f0f7fb; border-left: 4px solid #3498db; padding: 15px; border-radius: 4px; margin-bottom: 25px;'>\n")
  cat(params$ai_summary)
  cat("\n</div>\n\n")
}
```

## R Console Output

<div style="font-family: Consolas, 'Courier New', monospace; font-size: 10px; white-space: pre-wrap; background-color: #f8f9fa; padding: 10px; border: 1px solid #ccc; border-radius: 4px; line-height: 1.2;">
`r params$console_out`
</div>

## References

* Aiken, L. R. (1985). Three coefficients for analyzing the reliability and validity of ratings. *Educational and psychological measurement*, 45(1), 131-142.
* Djidu, H. (2026). measureR: Tools for Educational and Psychological Measurement. R package. Available at: https://github.com/hdmeasure/measureR
* Djidu, H. (2026). *measureR: Tools for educational and psychological measurement*. https://doi.org/10.32614/CRAN.package.measureR. R package.
* Lawshe, C. H. (1975). A quantitative approach to content validity. *Personnel psychology*, 28(4), 563-575.
* Polit, D. F., & Beck, C. T. (2006). The content validity index: are you sure you know what's being reported? Critique and recommendations. *Research in nursing & health*, 29(5), 489-497.

***
*Generated by measureR*
