---
title: "Classical Test Theory (CTT) Report"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    toc_depth: 2
params:
  ctt_res: NA
  dec: "."
  digits: 3
  console_out: NA
  ai_summary: ""
---

<style>
  body, p, table, td, th, li {
    font-family: 'Inter', 'Segoe UI', Roboto, Helvetica, Arial, sans-serif;
    line-height: 1.55;
    font-size: 14px;
    color: #333333;
  }
  h1, h2, h3, h4 { font-family: 'Inter', 'Segoe UI', Roboto, Helvetica, Arial, sans-serif; font-weight: 600; color: #2c3e50; }
  h1.title { font-size: 28px; border-bottom: 2px solid #ecf0f1; padding-bottom: 10px; }
  h2 { font-size: 22px; color: #2980b9; margin-top: 1.6em; }
  h3 { font-size: 17px; color: #34495e; }
  .cards { display: flex; flex-wrap: wrap; gap: 10px; margin: 10px 0 18px 0; }
  .card { flex: 1 1 140px; border: 1px solid #e2e8f0; border-top: 4px solid #0d6efd; border-radius: 8px; padding: 8px 12px; background: #fff; }
  .card .lab { font-size: 11px; color: #64748b; }
  .card .val { font-size: 24px; font-weight: 700; }
  .card .sub { font-size: 12px; color: #64748b; }
  .note { font-size: 12px; color: #64748b; }
  .callout { padding: 10px 14px; border-left: 4px solid #0d6efd; background: #f0f7ff; border-radius: 4px; margin: 10px 0; }
  .callout.warn { border-color: #fd7e14; background: #fff7ed; }
  .callout.bad { border-color: #dc3545; background: #fef2f2; }
  .callout.ok { border-color: #198754; background: #f0fdf4; }
  details { margin: 6px 0; }
  summary { cursor: pointer; font-weight: 600; }
  pre.console { font-size: 11px; background: #f8f9fa; border: 1px solid #ccc; border-radius: 4px; padding: 10px; white-space: pre-wrap; }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)
library(knitr)
library(kableExtra)
library(ggplot2)

res  <- params$ctt_res
dec  <- params$dec
dg   <- as.integer(params$digits)
ok   <- is.list(res) && !is.null(res$item_eval)

fmt <- function(x, digits = dg) {
  out <- rep("n/a", length(x))
  k <- !is.na(x)
  out[k] <- formatC(x[k], format = "f", digits = digits, decimal.mark = dec)
  out
}
ax <- function(x) format(x, decimal.mark = dec)

alpha_label <- function(a) {
  if (is.na(a)) "Not available" else if (a >= .90) "Excellent" else if (a >= .80) "Good" else
    if (a >= .70) "Acceptable" else if (a >= .60) "Questionable" else if (a >= .50) "Poor" else "Unacceptable"
}
alpha_col <- function(a) {
  if (is.na(a)) "#6c757d" else if (a >= .90) "#198754" else if (a >= .80) "#2e9e4f" else
    if (a >= .70) "#e0a800" else if (a >= .60) "#fd7e14" else if (a >= .50) "#dc3545" else "#a71d2a"
}
card <- function(lab, val, sub = "", col = "#0d6efd") {
  sprintf("<div class='card' style='border-top-color:%s'><div class='lab'>%s</div><div class='val' style='color:%s'>%s</div><div class='sub'>%s</div></div>",
          col, lab, col, val, sub)
}
rec_bg  <- function(x) ifelse(x == "Retain", "#d4edda", ifelse(x == "Revise", "#fff3cd", "#f8d7da"))
disc_bg <- function(x) ifelse(x %in% c("Very good", "Good"), "#d4edda", ifelse(x == "Marginal", "#fff3cd", "#f8d7da"))
diff_bg <- function(x) ifelse(x == "Moderate", "#d4edda", "#fff3cd")
```

```{r nores, results='asis', eval=!ok}
cat("<div class='callout bad'>No CTT results available. Run the analysis in the app before generating the report.</div>")
```

```{r prep, eval=ok}
ev   <- res$item_eval
n_ret <- sum(ev$Recommendation == "Retain", na.rm = TRUE)
n_rev <- sum(ev$Recommendation == "Revise", na.rm = TRUE)
n_eli <- sum(ev$Recommendation == "Eliminate / revise", na.rm = TRUE)
n_up  <- sum(ev$Raises_Alpha, na.rm = TRUE)
neg   <- ev$Item[!is.na(ev$Discrimination) & ev$Discrimination < 0]
ci    <- res$scaleMean + c(-1, 1) * 1.96 * res$SEM
```

# Overview {.unnumbered}

```{r overview, results='asis', eval=ok}
cat(sprintf("<p><b>Data:</b> %s &middot; <b>Item type:</b> %s &middot; <b>Examinees:</b> %s &middot; <b>Items:</b> %s</p>",
            ifelse(is.null(res$data_label), "-", res$data_label), res$type, res$nPerson, res$nItem))
cat("<div class='cards'>")
cat(card("Cronbach's &alpha;", fmt(res$alpha), alpha_label(res$alpha), alpha_col(res$alpha)))
cat(card("SEM", fmt(res$SEM), "score units"))
cat(card("Mean total score", fmt(res$scaleMean, 2), paste0("SD = ", fmt(res$scaleSD, 2)), "#0f766e"))
if (!is.na(res$split$sb)) cat(card("Split-half (S-B)", fmt(res$split$sb), alpha_label(res$split$sb), alpha_col(res$split$sb)))
cat(card("Items to review", n_rev + n_eli, "revise / eliminate", if (n_rev + n_eli == 0) "#198754" else "#dc3545"))
cat("</div>")

cat(sprintf("<div class='callout %s'><b>Summary.</b> The test (%d items, %d examinees) has Cronbach's &alpha; = %s (%s reliability) and SEM = %s; an observed score is expected to lie within &plusmn;1.96 &times; SEM of the true score 95%% of the time. Of the %d items, %d are retained, %d need revision and %d should be eliminated or revised (based on discrimination). %s%s</div>",
  if (is.na(res$alpha) || res$alpha >= .70) "ok" else "warn",
  res$nItem, res$nPerson, fmt(res$alpha), tolower(alpha_label(res$alpha)), fmt(res$SEM),
  res$nItem, n_ret, n_rev, n_eli,
  if (n_up > 0) sprintf("Removing %d item(s) (%s) would raise alpha. ", n_up, paste(ev$Item[ev$Raises_Alpha], collapse = ", ")) else "",
  if (length(neg) > 0) sprintf("Items with negative discrimination: %s; check the key or reverse-coded items.", paste(neg, collapse = ", ")) else ""))
```

# Reliability

```{r reliability, eval=ok}
rel <- data.frame(
  Statistic = c("Cronbach's alpha", "Interpretation", "SEM", "95% band around the mean score",
                "Split-half r (odd-even)", "Spearman-Brown corrected"),
  Value = c(fmt(res$alpha), alpha_label(res$alpha), fmt(res$SEM),
            paste0(fmt(ci[1], 2), " – ", fmt(ci[2], 2)),
            fmt(res$split$r), fmt(res$split$sb)),
  stringsAsFactors = FALSE
)
kable(rel, format = "html") %>% kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

<p class="note">Alpha interpretation: George and Mallery (2003); Nunnally and Bernstein (1994). SEM = SD &times; &radic;(1 &minus; &alpha;).</p>

```{r aid, eval=ok, fig.height=3.8, fig.width=8}
d <- ev
d$Item <- factor(d$Item, levels = d$Item)
ggplot(d, aes(Item, Alpha_if_Deleted, fill = Raises_Alpha)) +
  geom_col(width = .7) +
  geom_hline(yintercept = res$alpha, linetype = "dashed", colour = "#dc3545") +
  scale_fill_manual(values = c(`FALSE` = "#0d6efd", `TRUE` = "#dc3545"),
                    labels = c(`FALSE` = "Keep", `TRUE` = "Raises alpha if deleted"), name = NULL) +
  scale_y_continuous(labels = ax) +
  coord_cartesian(ylim = c(max(0, min(d$Alpha_if_Deleted, na.rm = TRUE) - .05), NA)) +
  labs(x = NULL, y = "Alpha if item deleted", subtitle = paste0("Dashed line: overall alpha = ", fmt(res$alpha))) +
  theme_minimal() + theme(axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1), legend.position = "bottom")
```

# Item Analysis

```{r items, eval=ok}
show_bis <- res$type == "dichotomous"
tab <- data.frame(
  Item = ev$Item,
  Mean = fmt(ev$Mean),
  p = fmt(ev$Difficulty),
  Difficulty = ev$Difficulty_Level,
  `Item-Total r` = fmt(ev$Discrimination),
  Discrimination = ev$Discrimination_Level,
  Biserial = fmt(ev$Biserial),
  `Alpha if Deleted` = fmt(ev$Alpha_if_Deleted),
  `Raises Alpha` = ifelse(ev$Raises_Alpha, "Yes", "No"),
  Recommendation = ev$Recommendation,
  check.names = FALSE, stringsAsFactors = FALSE
)
if (!show_bis) tab$Biserial <- NULL
cn <- colnames(tab)
kable(tab, format = "html", row.names = FALSE, align = "lrrlrlrrcl") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = TRUE) %>%
  column_spec(which(cn == "Difficulty"), background = diff_bg(ev$Difficulty_Level)) %>%
  column_spec(which(cn == "Discrimination"), background = disc_bg(ev$Discrimination_Level)) %>%
  column_spec(which(cn == "Raises Alpha"), background = ifelse(ev$Raises_Alpha, "#f8d7da", "#ffffff")) %>%
  column_spec(which(cn == "Recommendation"), background = rec_bg(ev$Recommendation), bold = TRUE)
```

<details>
<summary>Cut-offs used</summary>

* **Discrimination** (item-total correlation; Ebel and Frisbie, 1991): &ge; .40 very good; .30&ndash;.39 good; .20&ndash;.29 marginal (revise); < .20 poor (eliminate or revise); negative values suggest a keying error.
* **Difficulty p** (Allen and Yen, 1979; Crocker and Algina, 1986): < .30 difficult; .30&ndash;.70 moderate; > .70 easy. For polytomous items p = (mean &minus; min) / (max &minus; min).
* **Recommendation** is based on discrimination; "Raises Alpha" marks items whose removal would increase Cronbach's alpha.
</details>

```{r scatter, eval=ok, fig.height=4.2, fig.width=7}
d <- ev
ggplot(d, aes(Difficulty, Discrimination, colour = Recommendation, label = Item)) +
  annotate("rect", xmin = .30, xmax = .70, ymin = -Inf, ymax = Inf, fill = "#198754", alpha = .07) +
  geom_hline(yintercept = c(.20, .30), linetype = "dashed", colour = "grey55") +
  geom_point(size = 3) +
  geom_text(vjust = -1, size = 3, show.legend = FALSE, check_overlap = TRUE) +
  scale_colour_manual(values = c("Retain" = "#198754", "Revise" = "#e0a800", "Eliminate / revise" = "#dc3545")) +
  scale_x_continuous(labels = ax, limits = c(0, 1)) + scale_y_continuous(labels = ax) +
  labs(x = "Difficulty (p)", y = "Discrimination (item-total r)",
       subtitle = "Shaded band: p = .30–.70; dashed lines: r = .20 and .30") +
  theme_minimal() + theme(legend.position = "bottom")
```

```{r distractors, results='asis', eval=ok && !is.null(res$distractor)}
cat("# Distractor Analysis\n\n")
cat("<p class='note'>Option chosen by < 5% of examinees = non-functioning; an option with a positive option-total correlation needs review (Haladyna and Downing, 1993). The key is marked with *.</p>\n")
issues <- lapply(names(res$distractor), function(it) {
  df <- res$distractor[[it]]
  dis <- df[df$correct != "*", , drop = FALSE]
  data.frame(Item = it,
             `Non-functioning` = paste(rownames(dis)[dis$rspP < .05], collapse = ", "),
             `Positive option-total r` = paste(rownames(dis)[!is.na(dis$pBis) & dis$pBis > 0], collapse = ", "),
             check.names = FALSE, stringsAsFactors = FALSE)
})
issues <- do.call(rbind, issues)
flag <- issues[issues$`Non-functioning` != "" | issues$`Positive option-total r` != "", , drop = FALSE]
if (nrow(flag) == 0) {
  cat("<div class='callout ok'>All distractors are functioning.</div>\n")
} else {
  cat(kable(flag, format = "html", row.names = FALSE) %>%
        kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE))
}
cat("\n<details><summary>Full distractor tables (all items)</summary>\n")
for (it in names(res$distractor)) {
  df <- res$distractor[[it]]
  out <- cbind(Option = rownames(df), df)
  num <- vapply(out, is.numeric, logical(1)); num[c("n")] <- FALSE
  out[num] <- lapply(out[num], fmt)
  cat(sprintf("<h4>%s</h4>", it))
  cat(kable(out, format = "html", row.names = FALSE) %>%
        kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE, font_size = 12) %>%
        row_spec(which(df$correct == "*"), background = "#d4edda", bold = TRUE))
}
cat("</details>\n")
```

# Score Distribution

```{r hist, eval=ok, fig.height=3.6, fig.width=7}
sc <- res$score
ggplot(data.frame(Score = sc), aes(Score)) +
  geom_histogram(bins = max(5, min(30, diff(range(sc, na.rm = TRUE)) + 1)),
                 fill = "#0d6efd", color = "white", alpha = .85) +
  geom_vline(xintercept = mean(sc, na.rm = TRUE), colour = "#dc3545", linetype = "dashed") +
  scale_x_continuous(labels = ax) + scale_y_continuous(labels = ax) +
  labs(x = "Total score", y = "Frequency", subtitle = "Dashed line: mean") + theme_minimal()
```

```{r desc, eval=ok}
dd <- res$desc
dd$Value <- ifelse(dd$Statistic == "N", as.character(dd$Value), fmt(dd$Value))
kable(dd, format = "html", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

# Person Scores with SEM Band

```{r person, eval=ok}
ps <- res$person
n_show <- min(20, nrow(ps))
out <- data.frame(
  Respondent = seq_len(n_show),
  Score = fmt(ps$Score, 2),
  `95% band` = paste0(fmt(ps$Lower[1:n_show], 2), " – ", fmt(ps$Upper[1:n_show], 2)),
  `Estimated true score` = fmt(ps$True_Score[1:n_show], 2),
  `True score 95% band` = paste0(fmt(ps$True_Lower[1:n_show], 2), " – ", fmt(ps$True_Upper[1:n_show], 2)),
  check.names = FALSE, stringsAsFactors = FALSE
)
kable(out, format = "html", row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

<p class="note">First `r if (ok) min(20, nrow(res$person)) else 0` of `r if (ok) nrow(res$person) else 0` examinees; export the full table from the app. Observed band = X &plusmn; 1.96 &times; SEM (Crocker and Algina, 1986). Estimated true score (Kelley, 1923): T&#770; = &alpha;(X &minus; M) + M, with band T&#770; &plusmn; 1.96 &times; SD &times; &radic;(&alpha;(1 &minus; &alpha;)).</p>

```{r ai-summary, results='asis'}
if (!is.null(params$ai_summary) && !identical(params$ai_summary, "") && !is.na(params$ai_summary)) {
  cat("# AI Interpretive Summary\n\n")
  cat("<div class='callout'>\n")
  cat(params$ai_summary)
  cat("\n</div>\n\n")
}
```

# R Console Output

```{r console, results='asis'}
txt <- if (is.null(params$console_out) || all(is.na(params$console_out))) "" else params$console_out
cat("<pre class='console'>", htmltools::htmlEscape(txt), "</pre>")
```

# References

* Allen, M. J., & Yen, W. M. (1979). *Introduction to measurement theory*. Brooks/Cole.
* Crocker, L., & Algina, J. (1986). *Introduction to classical and modern test theory*. Holt, Rinehart & Winston.
* Ebel, R. L., & Frisbie, D. A. (1991). *Essentials of educational measurement* (5th ed.). Prentice Hall.
* George, D., & Mallery, P. (2003). *SPSS for Windows step by step* (4th ed.). Allyn & Bacon.
* Haladyna, T. M., & Downing, S. M. (1993). How many options is enough for a multiple-choice test item? *Educational and Psychological Measurement, 53*(4), 999&ndash;1010.
* Kelley, T. L. (1923). *Statistical method*. Macmillan.
* Nunnally, J. C., & Bernstein, I. H. (1994). *Psychometric theory* (3rd ed.). McGraw-Hill.
* Willse, J. T. (2018). *CTT: Classical test theory functions*. R package.
* Djidu, H. (2026). *measureR: Tools for educational and psychological measurement*. https://github.com/hdmeasure/measureR

***
*Generated by measureR*
