---
title: "Classical Test Theory (CTT) Report"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
params:
  ctt_res: NA
  console_out: NA
  ai_summary: ""
---

<style>
  @import url('https://fonts.googleapis.com/css2?family=Inter:wght@400;500;600;700&display=swap');
  
  body, p, table, td, th {
    font-family: 'Inter', 'Segoe UI', Roboto, Helvetica, Arial, sans-serif;
    line-height: 1.6 !important;
    font-size: 14px;
    color: #333333;
  }
  h1, h2, h3, h4, h5, h6 {
    font-family: 'Inter', 'Segoe UI', Roboto, Helvetica, Arial, sans-serif;
    line-height: 1.2;
    font-weight: 600;
    color: #2c3e50;
    margin-top: 1.5em;
    margin-bottom: 0.5em;
  }
  h1 { font-size: 28px; border-bottom: 2px solid #ecf0f1; padding-bottom: 10px; }
  h2 { font-size: 22px; color: #2980b9; }
  h3 { font-size: 18px; color: #34495e; }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(CTT)
library(dplyr)
library(knitr)
library(kableExtra)
```

## Scale Reliability and Summary

```{r}
res <- params$ctt_res
if(!is.null(res)){
  df_sum <- data.frame(
    Statistic = c("Scale Mean", "Scale SD", "Alpha (Cronbach)", "SEM", "N Items", "N Persons"),
    Value = c(
      round(res$scaleMean, 3),
      round(res$scaleSD, 3),
      round(res$alpha, 3),
      round(res$SEM, 3),
      ncol(res$itemReport),
      nrow(res$score)
    )
  )
  kable(df_sum, format = "html") %>% 
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
} else {
  cat("No CTT results available.")
}
```

## Item Analysis

```{r}
if(!is.null(res)){
  item_rep <- res$itemReport
  kable(item_rep, format = "html", digits = 3) %>% 
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE)
}
```

```{r ai-summary, results='asis'}
if (!is.null(params$ai_summary) && params$ai_summary != "") {
  cat("## AI Interpretive Summary\n\n")
  cat("<div style='background-color: #f0f7fb; border-left: 4px solid #3498db; padding: 15px; border-radius: 4px; margin-bottom: 25px;'>\n")
  cat(params$ai_summary)
  cat("\n</div>\n\n")
}
```

## R Console Output

<div style="font-family: Consolas, 'Courier New', monospace; font-size: 10px; white-space: pre-wrap; background-color: #f8f9fa; padding: 10px; border: 1px solid #ccc; border-radius: 4px; line-height: 1.2;">
`r params$console_out`
</div>

## References

* Djidu, H. (2026). measureR: Tools for Educational and Psychological Measurement. R package. Available at: https://github.com/hdmeasure/measureR
* Djidu, H. (2026). *measureR: Tools for educational and psychological measurement*. https://doi.org/10.32614/CRAN.package.measureR. R package.
* Lord, F. M., & Novick, M. R. (1968). *Statistical theories of mental test scores*. Addison-Wesley.

***
*Generated by measureR*
